---
title: "Preprocesamiento de datos kobo"
output:
  html_document:
    df_print: paged
---

```{r, message=FALSE}
library(dplyr)
library(tidyr)
```

Data exported from kobo need to be processed to a tidy format that R can manipulate more easily. 

## Trees sampling

Trees sampling was done by the 12 brigadistas in 48 plots of 10 x 10 m, using a kobo form.

### Load data and check for basic errors

```{r}
# load data
muestreo<-read.delim("../data/kobo/muestreo_dic2020_raw.txt", header = TRUE) %>%
# filter rows w/o actual data
  dplyr::filter(., !is.na(plot)) %>%

# remove unnecesary columns
  select(., -coordinates, -X__version__, -X_version_, -X_id, -X_uuid, -(X_index:X.6))
head(muestreo)
```

Create sample ID concateneting brigadista id + tree number (which were separate questions in kobo):

```{r}
muestreo$tree_id<-paste0(muestreo$person_key, muestreo$tree_number)
```

Check how many trees were sampled:

```{r}
# total
nrow(muestreo)

# dead / alive
table(muestreo$life_condition)

# by brigadista
table(muestreo$person_key)

# by plot
table(muestreo$plot)
```

We only sampled 48 plots, any larger number must be a typo during sampling. Check, and if there is an error, ommit those samples:

```{r}
# check
filter(muestreo, plot > 48) %>% select(plot, person_key, life_condition, tree_id)

# filter from data
muestreo <- filter(muestreo, !plot >48)
```
### Examine and clean tree health data

The variables `tree_health.*` are the result of a multiple choice question according to the tree health state. A single tree can have more than one type of damage.

```{r}
head(select(muestreo, tree_health.healthy:tree_health.other))
```

Change 0 - 1 notation for condition name:

```{r}
# 1 for healthy 
muestreo$tree_health.healthy= gsub("1", "healthy", as.character(muestreo$tree_health.healthy))
muestreo$tree_health.ozone= gsub("1", "ozone", as.character(muestreo$tree_health.ozone))
muestreo$tree_health.fungi= gsub("1", "fungi", as.character(muestreo$tree_health.fungi))
muestreo$tree_health.drougth= gsub("1", "drougth", as.character(muestreo$tree_health.drougth))
muestreo$tree_health.worm= gsub("1", "worm", as.character(muestreo$tree_health.worm))
muestreo$tree_health.insect= gsub("1", "insect", as.character(muestreo$tree_health.insect))
muestreo$tree_health.acid_rain= gsub("1", "acid_rain", as.character(muestreo$tree_health.acid_rain))
muestreo$tree_health.other= gsub("1", "other", as.character(muestreo$tree_health.other))

# 0 for NA
muestreo$tree_health.healthy= gsub("0", NA, as.character(muestreo$tree_health.healthy))
muestreo$tree_health.ozone= gsub("0", NA, as.character(muestreo$tree_health.ozone))
muestreo$tree_health.fungi= gsub("0", NA, as.character(muestreo$tree_health.fungi))
muestreo$tree_health.drougth= gsub("0", NA, as.character(muestreo$tree_health.drougth))
muestreo$tree_health.worm= gsub("0", NA, as.character(muestreo$tree_health.worm))
muestreo$tree_health.insect= gsub("0", NA, as.character(muestreo$tree_health.insect))
muestreo$tree_health.acid_rain= gsub("0", NA, as.character(muestreo$tree_health.acid_rain))
muestreo$tree_health.other= gsub("0", NA, as.character(muestreo$tree_health.other))

# check
head(select(muestreo, tree_health.healthy:tree_health.other))
```

The original `tree_health` variable concatenates kobo answers, but it changes depending in the order the options were selected, so lets create a new variable concatenanting from the binary `tree_heath.*` variables

```{r}
# use useful fuction found in https://stackoverflow.com/questions/13673894/suppress-nas-in-paste
paste5 <- function(..., sep = " ", collapse = NULL, na.rm = F) {
  if (na.rm == F)
    paste(..., sep = sep, collapse = collapse)
  else
    if (na.rm == T) {
      paste.na <- function(x, sep) {
        x <- gsub("^\\s+|\\s+$", "", x)
        ret <- paste(na.omit(x), collapse = sep)
        is.na(ret) <- ret == ""
        return(ret)
      }
      df <- data.frame(..., stringsAsFactors = F)
      ret <- apply(df, 1, FUN = function(x) paste.na(x, sep))

      if (is.null(collapse))
        ret
      else {
        paste.na(ret, sep = collapse)
      }
    }
}

# paste to concatenate in new variable
muestreo$tree_health <- paste5(muestreo$tree_health.healthy, 
                        muestreo$tree_health.ozone, 
                        muestreo$tree_health.fungi,
                        muestreo$tree_health.drougth,
                        muestreo$tree_health.worm,
                        muestreo$tree_health.insect,
                        muestreo$tree_health.acid_rain,
                        muestreo$tree_health.other,
                        na.rm=TRUE)
# check
head(muestreo$tree_health)
```

Check combinations of damage:

```{r}
unique(muestreo$tree_health)
```

We can't have "healthy + a damage condition". If this appears this is an error made during sampling. If this happens we have to check the photos of this entries to correct accordingly. All values of "healthy + a damage" will be ommited from the data.


```{r}
# check if there are any trees with healthy + other. If this is the case, there should be an " " after healthy
muestreo[grep("healthy ", muestreo$tree_health), c("plot", "tree_id")]

# remove any tree labeled with healthy + something else
muestreo<-muestreo[grep("healthy ", muestreo$tree_health, invert=TRUE), ]

# check
unique(muestreo$tree_health)
```

Make a new variable to collapse the interaction of ozone + others in a single variable. This would be useful for visualization purposes:

```{r}
# collapse together interactions of ozone + others
muestreo <- muestreo %>%
            mutate(., tree_health_simplified = ifelse(grepl("ozone ", tree_health), "ozone_and_other", tree_health)) %>% 

# collapse together other types of damage
            mutate(., tree_health_simplified = ifelse(grepl(" ", tree_health_simplified), "others_combined", tree_health_simplified))

#check
head(muestreo$tree_health_simplified)
table(muestreo$tree_health_simplified)
```

Samples with `NA` in `tree_health_simplified` are actually dead trees:

```{r}
filter(muestreo, is.na(tree_health_simplified)) %>% select(life_condition)
```

Change "NA" to "dead" in tree_health_simplified`:

```{r}
muestreo<- mutate(muestreo, 
                  tree_health_simplified=  replace_na(tree_health_simplified, "dead"))
table(muestreo$tree_health_simplified)
```

Columns with presence/absence health condition data are no longer needed, remove them
```{r}
muestreo<- select(muestreo, 
                  -c(tree_health.healthy:tree_health.other))
```

#### Clean percentage of ozone damage by tree

To be done

## Sampling plots

Plots metadata was surveyed by Alicia Mastretta using another kobo form.

#### Load data and check

```{r}
parcelas<-read.delim("../data/kobo/parcelas_dic2020_raw.txt", header=TRUE) %>%

# remove unnecesary columns
  select(., -coordinates, -X__version__, -X_version_, -X_id, -X_uuid, -X_index)
parcelas
```

#### Clean reforestation notes and dominant spp

To be done.

#### Add summary of tree health by plot

First make a summary of tree health from the sampling form:

```{r}
#Make summary 
plots_health <- group_by(muestreo, plot) %>%
                         summarise(tree_health_simplified) %>%
  
# Pivot wider 
                pivot_wider(names_from = tree_health_simplified,
                            values_from = tree_health_simplified,
                            values_fn = length) %>%
                  
# replace na with 0 
                replace(is.na(.), 0)

plots_health
```

Then add this summary to the parcelas form:

```{r}
# join tables
parcelas<-inner_join(parcelas, plots_health, by = "plot")
```


## Save tidy data

Remove unused columns

```{r}
# from parcelas
parcelas<- select(parcelas, 
                  -c(dominant_spp.Pinus_ayacauite:dominant_spp_others),
                  -X_submission_time)
```


Save data
```{r}
write.table(muestreo, file="../data/kobo/muestreo_dic2020_tidy.txt", sep ="\t")
write.table(parcelas, file="../data/kobo/parcelas_dic2020_tidy.txt", sep ="\t")
```



