---
title: "R Notebook"
output:
  html_document:
    df_print: paged
---

This document presents the subset of the figures used for paper about monitoring.

## Data and packages

```{r, message=FALSE, warning=FALSE}
library(dplyr)
library(tidyr)
library(ggplot2)
library(ggmap)
library(scatterpie)
library(rgdal)
```


Sampling data correspond to the data collected with kobo and previously cleaned with the script `1_preprocesamiento_datos_kobo.Rmd`.

```{r, message=FALSE}
# load data
muestreo_tidy<-read.delim("../data/kobo/muestreo_dic2020_tidy.txt", header = TRUE)
parcelas_tidy<-read.delim("../data/kobo/parcelas_dic2020_tidy.txt", header = TRUE)

# pivot long parcelas data to have health data as a single variable
parcelas_long<-pivot_longer(parcelas_tidy, 
                            cols = healthy:worm, 
                            names_to = "tree_health_simplified",
                            values_to = "n_trees")
```

Data analyzed here correspond only to the trees that were approved during the validation by manually reviewing the photographs in kobotoolbox. Total of `r nrow (muestreo_tidy)` trees sampled, `r sum (muestreo_tidy$X_validation_status=="validation_status_approved")` were approved in the validation.

```{r}
muestreo_tidy<- filter(muestreo_tidy, X_validation_status=="validation_status_approved")
```

Color palettes:

```{r, message=FALSE}
# Make a nice color pallete and legend order for all plots

my_cols=c("darkgreen", 
              "darkred", 
              "orangered1", 
              "cadetblue", 
              "tan", 
              "beige", 
            #  "burlywood4", 
              "coral", 
              "aquamarine3", 
              "gray70", 
              "black")

desired_order=c("healthy", 
                "ozone", 
                "ozone_and_other", 
                "others_combined", 
                "drougth", 
                "fungi", 
             #   "insect", 
                "worm", 
                "acid_rain", 
                "other", 
                "dead")

desired_names=c("healthy", 
                "ozone", 
                "ozone and other", 
                "others combined", 
                "drougth", 
                "fungi", 
             #   "insect", 
                "worm", 
                "acid rain", 
                "other", 
                "dead")

# For ozone damage percentage 
 my_cols2<-c("gold2", "chocolate1", "orangered", "red4", "darkorchid4")
 
desired_order_percentage<-c("less than 10%", "10 to 40%", "40 to 50%", "50 to 70%", "more than 70%")


```

Multiplot fun:

```{r}
# Multiple plot function
#
# ggplot objects can be passed in ..., or to plotlist (as a list of ggplot objects)
# - cols:   Number of columns in layout
# - layout: A matrix specifying the layout. If present, 'cols' is ignored.
#
# If the layout is something like matrix(c(1,2,3,3), nrow=2, byrow=TRUE),
# then plot 1 will go in the upper left, 2 will go in the upper right, and
# 3 will go all the way across the bottom.
#
multiplot <- function(..., plotlist=NULL, file, cols=1, layout=NULL) {
  library(grid)

  # Make a list from the ... arguments and plotlist
  plots <- c(list(...), plotlist)

  numPlots = length(plots)

  # If layout is NULL, then use 'cols' to determine layout
  if (is.null(layout)) {
    # Make the panel
    # ncol: Number of columns of plots
    # nrow: Number of rows needed, calculated from # of cols
    layout <- matrix(seq(1, cols * ceiling(numPlots/cols)),
                    ncol = cols, nrow = ceiling(numPlots/cols))
  }

 if (numPlots==1) {
    print(plots[[1]])

  } else {
    # Set up the page
    grid.newpage()
    pushViewport(viewport(layout = grid.layout(nrow(layout), ncol(layout))))

    # Make each plot, in the correct location
    for (i in 1:numPlots) {
      # Get the i,j matrix positions of the regions that contain this subplot
      matchidx <- as.data.frame(which(layout == i, arr.ind = TRUE))

      print(plots[[i]], vp = viewport(layout.pos.row = matchidx$row,
                                      layout.pos.col = matchidx$col))
    }
  }
}
```

Configure google api for maps:

``` {r}
# code adapted from https://rgraphgallery.blogspot.com/2013/04/rg-plot-pie-over-g0ogle-map.html

## configure google api

# You first need to register your api key in https://cloud.google.com/maps-platform/#get-started and follow instructions. The geocoding API is a free service, but you nevertheless need to associate a credit card with the account. Please note that the Google Maps API is not a free service. There is a free allowance of 40,000 calls to the geocoding API per month, and beyond that calls are $0.005 each.
# after you obtain your api, save it in /scripts/api_key.api (not shown in this repo por obvious reasons).

# if you get the following error when running get_map():

#"Error in aperm.default(map, c(2, 1, 3)) : 
#  invalid first argument, must be an array " 

# check this troubleshooting: https://rgraphgallery.blogspot.com/2013/04/rg-plot-pie-over-google-map.html

##  load and register api
api <- readLines("api_key.api")
register_google(key = api)
```

# Map and monitoring figures presented in the paper:

# Figure 2

## PNDL location on CDMX map

```{r, fig.height=6, fig.width=6, message=FALSE}
# get cdmx shape
CDMX<-readOGR(dsn="../data/spatial", layer="CDMX")
CDMX<-fortify(CDMX)

# get PNDL shape
PNDL<-readOGR(dsn="../data/spatial", layer="Desierto_Leones_Geo_ITRF08")
PNDL<-fortify(PNDL)

# get background map
sat_map = get_map(location = c(lon = -99.133549, lat = 19.3), zoom = 10, maptype = 'terrain-background', source = "google")

## plot
p_a<-ggmap(sat_map) + 
            geom_polygon(data = CDMX,
                         aes(x = long, y = lat, group = group),
                         color="black", fill=NA, size=1.5) +
            geom_polygon(data = PNDL,
                         aes(x = long, y = lat, group = group),
                         color="red", fill=NA, size=1.5) +
            geom_point(aes(x=-98.95, y=19.6), 
                       shape=0, stroke=2, size=5, color="black") +
            geom_point(aes(x=-98.95, y=19.55), 
                       shape=0, stroke=2, size=5, color="red") +
            geom_text(aes(label="CDMX", x=-98.87, y=19.6), 
                      color="Black", fontface="bold", size=5) +
            geom_text(aes(label="PNDL", x=-98.87, y=19.55), 
                      color="Black", fontface="bold", size=5) +
            theme(text = element_text(size = 20))+
  ggtitle("a)")
```

## Satellite image and surroundings of the PNDL
```{r, fig.height=6, fig.width=6, message=FALSE}
# get background map
sat_map = get_map(location = c(lon = -99.30, lat = 19.31), zoom = 13, maptype = 'satellite', source = "google")

## add towns names
towns<-data.frame(nombre=c("San Bartolo Ameyalco", 
                           "Santa Rosa Xochiac", 
                           "San Mateo Tlaltenango"),
                  long=c(-99.270, -99.29, -99.276),
                  lat=c(19.333, 19.325, 19.346))



## plot
p_b<-ggmap(sat_map) + 
            geom_polygon(data = PNDL,
                         aes(x = long, y = lat, group = group),
                         color="red", fill=NA, size=1.5) +
            geom_point(data=towns, aes(x=long, y=lat), colour="red", size=1.5) +
            geom_text(data=towns, aes(label=nombre, x=long, y=lat), 
                      color="white", fontface="bold",
                      size=5, nudge_y=0.003) +
  # add Cruz de Coloxtitla (CX), and Convento (Cn) landmarks
            geom_text(aes(label="X", x=-99.3014, y=19.286068), 
                      color="white", fontface="bold", size=4) +
            geom_text(aes(label="C", x=-99.31, y=19.3133), 
                      color="white", fontface="bold", size=4) +
            theme(text = element_text(size = 20))+
  ggtitle("b)")
```

## This is the distribution of the 48 plots:

```{r, message=FALSE, fig.height=15, fig.width=15}

## plot map
# get map
sat_map = get_map(location = c(lon = -99.3060, lat = 19.2909), zoom = 14, maptype = 'satellite', source = "google")

# plot sampled plots
p_c <-  ggmap(sat_map)
p_c <- p_c + geom_point(data=parcelas_tidy,
                      aes(x=X_coordinates_longitude,
                          y=X_coordinates_latitude),
                      color="red") +
          geom_text(data=parcelas_tidy,
                      aes(x=X_coordinates_longitude,
                          y=X_coordinates_latitude,
                          label=plot),
                      color="white",
                     check_overlap = TRUE,
                      hjust = 0, vjust=1, nudge_x = 0.0005,
                 size= 5) +
    theme(text = element_text(size = 20))+
  ggtitle("c)")
```

## Distribution of tree health status by plot

The following figure shows the total number of trees sampled in each 10x10 m plot, and how many of these are under some category of damage:

```{r, message=FALSE, fig.height=9, fig.width=11}
p_d <- ggplot(parcelas_long, aes(x=plot, y=n_trees,     fill=tree_health_simplified)) +
  geom_bar(stat="identity") +
  scale_fill_manual(values= my_cols, breaks = desired_order,
                    labels= desired_names,
                    name= "Health category") 
  

p_d <- p_d + theme_bw() +
  labs(x="Plots", y= "Number of trees") +
  theme(text = element_text(size = 20)) +
  ggtitle("d)")

```


Multiplot
```{r, message=FALSE, fig.height=12, fig.width=16}
multiplot(p_a, p_c, p_b, p_d, cols=2)
```

# Figure 3

```{r, message=FALSE, fig.height=9, fig.width=11}
p3 <- ggplot(muestreo_tidy, aes(x=tree_exposition, 
                      fill=tree_health_simplified)) +
       geom_bar(stat="count") +
  scale_fill_manual(values= my_cols, breaks = desired_order,
                    labels= desired_order,
                    name= "Status of healthy") +  
  facet_grid(. ~ reforested, 
             labeller = as_labeller(c("yes" = "reforested",
                                    "no" = "natural"))) +
  scale_x_discrete(breaks=c("cover", "exposed"),
        labels=c("cover", "exposed"))
p3 + theme_bw() +
     theme(plot.title = element_text(lineheight=1.1, face="bold")) +
  labs(x="", y= "Number of trees") +
  theme(text = element_text(size = 20)) 
```


# Figure 4

## Plot 4a

```{r, message=FALSE, fig.height=9, fig.width=11}
p <- filter(muestreo_tidy, tree_heigth<15, tree_nodes>0) %>% 
     ggplot(.) +
     scale_fill_manual(values= my_cols, breaks = desired_order,
                    labels= desired_order,
                    name= "Status of healthy") +
theme_bw()

p4_a <- p + geom_histogram(aes(x=tree_nodes, 
                      fill=tree_health_simplified))  +
    labs(x="Number of nodes", y= "Number of trees") +
    theme(text = element_text(size = 20)) +
     theme(plot.title = element_text(lineheight=1.1, face="bold"))+
  ggtitle("a)")

p4_a
  
  
```

## Plot 4b

```{r, fig.height=9, fig.width=13}
## base data
p_od<- muestreo_tidy %>% filter(!is.na(ozone_damage_percentage)) %>%
            ggplot() +
            scale_fill_manual(values= my_cols2, 
                              breaks = desired_order_percentage,
                              labels = c("less 10%", "10 to 40%", "40 to 50%",
                                         "50 to 70%", "more 70%"),
                              name= "Tree ozone damage percentage") +
            theme_bw() + theme(text = element_text(size = 20)) 

p4_b <- p_od +
  geom_bar(aes(x=tree_nodes,
               fill=ozone_damage_percentage)) +
  labs(x="Number of nodes", y= "Number of trees") +
  theme(plot.title = element_text(lineheight=1.1, face="bold"))+
  ggtitle("b)")
p4_b 

```

# Plot 4c
```{r, message=FALSE, fig.height=12, fig.width=16}

# Filtrar por categoría de daño
condition_HOO<-muestreo_tidy%>%
  filter(tree_health_simplified == "healthy" | tree_health_simplified == "ozone" | tree_health_simplified == "ozone_and_other" )

condition_HOO$tree_health_simplified <- as.factor(condition_HOO$tree_health_simplified)

# Plot
p4_c<-condition_HOO%>%
   ggplot(aes(y= tree_nodes, x= tree_health_simplified))+
          geom_boxplot(color="grey", notch = F)+
        scale_color_manual(values=  my_cols)+
        geom_point(position="jitter",aes(color = tree_health_simplified), alpha=0.5)+
    theme(axis.text.x=element_text(colour="black", size = 8, 
                                 angle = 45, vjust = 1, hjust = 1),
        axis.text.y=element_text(colour="black", size = 7, angle = 0))+
        xlab("Status of healthy")+ ylab("Tree nodes")+
  labs(color = "Status of healthy")+
  ggtitle("c)")
p4_c
```

# Plot 4d
```{r, message=FALSE, fig.height=12, fig.width=16}

# Plot

muestreo_tidy$ozone_damage_percentage
p4_d<-muestreo_tidy%>%
   ggplot(aes(y= tree_nodes, x= ozone_damage_percentage))+
          geom_boxplot(color="grey", notch = F)+
        scale_color_manual(values=  my_cols2)+
        geom_point(position="jitter",aes(color = ozone_damage_percentage), alpha=0.5)+
    theme(axis.text.x=element_text(colour="black", size = 8, 
                                 angle = 45, vjust = 1, hjust = 1),
        axis.text.y=element_text(colour="black", size = 7, angle = 0))+
        xlab("ozone damage percentage")+ ylab("Tree nodes")+
  labs(color = "ozone damage percentage")+
  ggtitle("d)")
p4_d
```


Multiplot
```{r, message=FALSE, fig.height=12, fig.width=16}
multiplot(p4_a, p4_c, p4_b, p4_d, cols=2)
```
